\huge Gap formation and stability in non-isothermal disks\\ \Large [2014 CITA Summer Student Program]

### 2014-07-22 poster/poster.tex
minor update to tex

            \begin{block}{{\Large Disk-planet model with simple cooling}}
             We numerically evolve the 2D fluid equations including a gap-opening giant planet, treated as an external potential on fixed circular orbit. We include in the energy equation
        a simple source term in the form
	\begin{align*}
	\frac{\partial e}{\partial t} = \cdots + \frac{e-e_{t=0}}{t_\mathrm{cool}},
	\end{align*}
        and $t_\mathrm{cool} = \beta \Omega_k^{-1}$, where $\Omega_k$ is the Keplerian frequency. We choose $\beta$ indirectly 
        through $\tilde{\beta}$ such that
        \begin{align*}
        t_\mathrm{cool, gap\,edge} = \tilde{\beta} t_\mathrm{lib, gap\,edge},
        \end{align*}
        where $t_\mathrm{lib, gap\,edge}$ is the time interval between successive encounters of a fluid element, 
        located at the gap edge, and the planet's azimuth. Thus $\tilde{\beta}\ll 1$ implies that such a fluid returns to its initial temperature
        before passing by the planet again. 
        \end{block}
        \vfill

            \begin{block}{{\Large The generalized potential vorticity}}
              \justifying
                  {\bf generalized vortensity profile due to planet for
                    different beta. also density profiles.}

                  \begin{figure}
                    \centering
                    \hfill
                    \begin{minipage}{0.49\textwidth}
                      \includegraphics[width=\textwidth]{Posterfig_Density}
                    \end{minipage}
                    \hfill
                    \begin{minipage}{0.49\textwidth}
                      \includegraphics[width=\textwidth]{Posterfig_Vortensity}
                    \end{minipage}
                    \hfill
                  \end{figure}

                  \begin{figure}
                    \centering
                    \includegraphics[width=0.5\textwidth]{Posterfig_HR}
                  \end{figure}

>>>>

            \begin{block}{{\Large Disk-planet model with simple
                  cooling}}
              \justifying
             We numerically evolve the 2D fluid equations including a
             gap-opening giant planet, treated as an external
             potential on fixed circular orbit. We include in the
             energy equation  
        a simple source term in the form 
	\begin{align*}
	\frac{\partial e}{\partial t} = \cdots + \frac{e-e_{t=0}}{t_\mathrm{cool}},
	\end{align*}
        and $t_\mathrm{cool} = \beta \Omega_k^{-1}$, where $\Omega_k$ is the Keplerian frequency. We choose $\beta$ indirectly 
        through $\tilde{\beta}$ such that
        \begin{align*}
        t_\mathrm{cool, gap\,edge} = \tilde{\beta} t_\mathrm{lib, gap\,edge},
        \end{align*}
        where $t_\mathrm{lib, gap\,edge}$ is the time interval between successive encounters of a fluid element, 
        located at the gap edge, and the planet's azimuth. Thus $\tilde{\beta}\ll 1$ implies that such a fluid returns to its initial temperature
        before passing by the planet again. 
        \end{block}
        \vfill

        \begin{block}{{\Large Planet gaps as a function of cooling
              rate}}
          \justifying
          % {\bf generalized vortensity profile due to planet for
          %   different beta. also density profiles.}

          \begin{figure}
            \centering
%            \hfill
%            \begin{minipage}{0.49\textwidth}
              \includegraphics[width=.49\textwidth]{Posterfig_Density}\\
%           \end{minipage}
%            \hfill
%            \begin{minipage}{0.49\textwidth}
              \includegraphics[width=.49\textwidth]{Posterfig_Vortensity}
%            \end{minipage}
%            \hfill
          \end{figure}

          %\begin{figure}
          %  \centering
          %  \includegraphics[width=0.5\textwidth]{Posterfig_HR}
          %\end{figure}
